Paper Notes

### 2017-12-10 paper_notes.tex
normal update

\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}	% make indent in first paragraph
\usepackage{bm}
\usepackage{geometry}		% to make typesettings like margins
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{natbib}			% to insert citations
\usepackage{xcolor}			% extend the colors can be used

\usepackage{bibentry}		% package used to insert full citation in body text
\nobibliography*

@@

\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section] % reset theorem numbering for each chapter
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition} % definition numbers are dependent on theorem numbers
\newtheorem{exmp}[thm]{Example} % same for example numbers
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{obs}{Observation}

@@

% A list of new commands
\newcommand{\R}{\mathbb{R}}			% depends on the package amssymb

@@

\tableofcontents{}
\setcounter{tocdepth}{1}			% show only parts, chapters, and sections in content

@@

@@

@@

There are several difficulties in estimating production functions which will cause endogeneity problem. To name some:
\begin{itemize}
	\item Simultaneouty. For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometrician. This could induce endogeneity when directly using OLS. Suppose $\omega_{it}$ has positive serial correlation, when $\omega_{it}$ is high, firm will choose higher input bacause it is very possible that $\omega$ in next period will be high as well. This induces a positive bias for $\beta_k$.
	\item Exit selection bias. When constructing a balanced panel, then we only observe those firms with high $\omega_{it}$.
\end{itemize}

@@

\begin{itemize}
	\item Classical Approach.
	\begin{itemize}
		\item Use input price as IV. The problem is input price is generally the same across firms. When we do observe different input prices, which generally indicates market power in input markets. Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
		\item Use fixed effect. We need to assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
	\end{itemize}
	\item Control Function for  $\omega_{it}$. This approach first raised by \cite{Olley:1996ef} and developed by \cite{Levinsohn:2003ej} and \cite{Ackerberg:2015ha}. We name them OP, LP, ACF here after. The key idea is to use a function of what we know (for example, $k_t$ and $i_{t-1}$ in OP) to proxy $\omega$, the existence of such function is guaranteed by the solutioin property of the firm optimization problem. And the specific form of this function is estimated nonparametrically.
	\begin{itemize}
		\item OP uses a two step estimation process. First step, use $k_t$ and $i_{t-1}$ nonparametrically estimate $\omega_t$, plug this into original production function then use OLS. Notice the unobserved $\omega_t$ has been controled by $k_t$ and $i_{t-1}$, then OLS will give consistent estimator for $l_t$ but not $k_t$. In second step, we first write $\omega_{it} = E[\omega_{it}|\omega_{it-1}]+\xi_{it}$, notice that $\xi_{it}$ is independent of any information set at t-1. Thus we get the moment condition $E[\xi_{it}k_{it}]=0$, then we can use method of simulating moments to estimate $\beta_k$.
		\item LP is very similar to OP, just that use intermediate input $m_{it}$ instead of investment $i_{it}$ in proxy $\omega_{it}$. Because OP approach requires the policy function of $i_{it}$ be monotonicity in $\omega_{it}$, which is unsatisfied when $i_{it}=0$. But data shows that in many observations $i=0$. Using intermediate input can solve this.
		\item ACF critizition is
	\end{itemize}
	\item \cite{Gandhi:2017un} Approach (GNR). GNR criticizes control function approach is nonparametrically not identified in the presence of flexible inputs. They raise a new approach using FOC conditions.
\end{itemize}

@@

@@

>>>>

\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}	% make indent in first paragraph
\usepackage{bm}
\usepackage{geometry}		% to make typesettings like margins
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{hyperref}

\usepackage{natbib}			% to insert citations
\usepackage{xcolor}			% extend the colors can be used
\usepackage{calrsfs}		% caligraphy font family

\usepackage{bibentry}		% package used to insert full citation in body text
\makeatletter 
\renewcommand\BR@b@bibitem[2][]{\BR@bibitem[#1]{#2}\BR@c@bibitem{#2}}
\makeatother
\nobibliography*

\usepackage{setspace}		% set space for comment bullet

@@

\usepackage{tocbibind}		% to add toc and bib into table of content
\usepackage{bookmark}	% to separate the last chapter from previous ones

\usepackage{amsthm}
\makeatletter
\def\th@plain{%
  \thm@notefont{}% same as heading font
  \itshape % body font
}
\def\th@definition{%
  \thm@notefont{}% same as heading font
  \normalfont % body font
}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section] % reset theorem numbering for each chapter
\theoremstyle{definition}
\newtheorem{defn}{Definition}[section] % definition numbers are dependent on theorem numbers
\newtheorem{exmp}{Example}[section] % same for example numbers
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{obs}{Observation}

\newenvironment{myproof}
{\noindent\textit{Proof:}}{\hfill$\square$}

@@

% A list of new commands
\newcommand{\R}{\mathbb{R}}			% depends on the package amssymb
\newcommand{\F}{\mathcal{F}}
\newcommand{\myline}{\vspace{3mm} \hrule \vspace{4mm}}

\usepackage{amsmath}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\tableofcontents{}
\label{toc}
\setcounter{tocdepth}{1}			% show only parts, chapters, and sections in content

\part{Economics}
\label{part:economics}

@@

\section{Gentzkow-Kelley-Taddy, 17 WP} % (fold)
\label{sec:gentzkow_kelley_taddy_17_wp}

\noindent
\textbf{\bibentry{Gentzkow_el.al:17WP}}

An survey paper on how text analysis can be used in economic research. 
The main difficulty is the high-dimensionality of text.

\noindent
Steps to reduce dimension:
\begin{enumerate}
	\item Represent raw text $\mathcal{D}$ as a numerical array $C$
	\begin{enumerate}
		\item Divide $\mathcal D$ into individual documents $\mathcal D_i$, the level is determined by the level of $V$. For example, daily attributes or monthly attributes.
		\item Feature Selection. Drop out punctuations, numbers, HTML tags, proper names and so on. Both very common and very rare words will be excluded. And words with the same stems will be reduced to one.
		\item Limit dependence between words using N-gram. The idea is to only consider consider phrase of length n.
	\end{enumerate}
	\item Map $C$ to predicted values $\hat V$ of unknown outcomes $V$
	\item Use $\hat V$ in subsequent descriptive or causla analysis
\end{enumerate}

\textcolor{blue}{Reading not finished.
\cite{grimmer_stewart_2013} also talks this problem. worth reading}
% section gentzkow_kelley_taddy_17_wp (end)

\section{Seminar Notes} % (fold)
\label{sec:seminar_notes}

\noindent
\textbf{AI and Economics}
(\url{http://taddylab.com/slides/EconAI.pdf})

This slides procides some clear intro on why and how AI (also deep learning) can be applied in economics.
Many references provided in slides as well.

\textcolor{blue}{Not understand much. Needs further reading.}

% section seminar_notes (end)

@@

\section{Data and Techniques} % (fold)
\label{sec:data_and_techniques}

\subsection{Data Source} % (fold)
\label{sub:data_source}

\noindent
\textbf{Uber and Taxi}
\begin{itemize}
	\item New York Taxi and Limousine Commission Trip Data
	\begin{itemize}
		\item \url{http://www.nyc.gov/html/tlc/html/about/trip_record_data.shtml}
		\item Literature: Bian Bo (JMP)
	\end{itemize}
\end{itemize}

% subsection data_source (end)

\subsection{Techniques} % (fold)
\label{sub:techniques}

% subsection techniques (end)

\noindent
\textbf{High Resolution Satelite Data:}
\begin{itemize}
	\item Pixel is as accurate as 0.5m, much finer than the Night Light data;
	\item Use machine learning to identify the roads, cars, buildings etc;
	\item Jonathan Hersh has a paper over this. \textbf{\href{https://www.dropbox.com/s/zeph7rrch2rwfwp/PovSpace_JMP_Oct31.pdf?dl=0}{Poverty from Space: Using High Resolution Satellite Imagery for Estimating Economic Well-being and Geographic Targeting}}
\end{itemize}

\myline

\noindent
\textbf{Paralelle Computation:}
\begin{itemize}
	\item A detailed cook manual on Paralelle computation of RBC model:

	\url{https://www.kellogg.northwestern.edu/researchcomputing/docs/ParallelComputing/ParallelizationForRBCModel.pdf}

	\item Another source: \url{https://bfi.uchicago.edu/sites/default/files/file_uploads/Lecture_Parallel_Programming_Chicago%20%282%29.pdf}
\end{itemize}

\myline

\noindent
\textbf{Text as Data:}
\begin{itemize}
	\item \href{run:resources/text_as_data}{Course Materials by Justin Grimmer}
	\item \bibentry{grimmer_stewart_2013}
	\item \bibentry{Gentzkow_el.al:17WP}
\end{itemize}

% section data_and_techniques (end)

@@

There are several difficulties in estimating production functions which will cause endogeneity problem. To name some:
\begin{itemize}
	\item Simultaneity. For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometricians. This could induce endogeneity when directly using OLS. 
	Suppose $\omega_{it}$ has \textit{positive serial correlation}, when $\omega_{it}$ is high, firm will choose higher input because it is very possible that $\omega$ in next period will be high as well. This induces a positive bias for $\beta_k$.
	\item Exit selection bias. When constructing a balanced panel, then we only observe those firms with high $\omega_{it}$.
	\textcolor{blue}{Why we have to construct a balanced panel?}
\end{itemize}

@@

\begin{itemize}
	\item Classical Approach.
	\begin{itemize}
		\item Use input price as IV. The problem is input price is generally the same across firms. When we do observe different input prices, which generally indicates market power in input markets. Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
		\begin{itemize}
			\item (My comment) When using input price as IV, we actually assume they are independent of productivities.
			This may not be the case.
			If productivity has some correlation across the firms,
			then it is possible that when productivity is high,
			the input price in the market will also be high.
		\end{itemize}
		\item Use fixed effect. We need to assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
	\end{itemize}
	\item Control Function for  $\omega_{it}$. This approach first raised by \cite{Olley:1996ef} and developed by \cite{Levinsohn:2003ej} and \cite{Ackerberg:2015ha}. We name them OP, LP, ACF here after. The key idea is to use a function of what we know (for example, $k_t$ and $i_{t-1}$ in OP) to proxy $\omega$, the existence of such function is guaranteed by the solutioin property of the firm optimization problem. And the specific form of this function is estimated non-parametrically.
	\begin{itemize}
		\item OP uses a two step estimation process. First step, use $k_t$ and $i_{t}$ non-parametrically estimate $\omega_t$, plug this into original production function then use OLS. Notice the unobserved $\omega_t$ has been controlled by $k_t$ and $i_{t}$, then OLS will give consistent estimator for $l_t$ but not $k_t$. In second step, we first write $\omega_{it} = E[\omega_{it}|\omega_{it-1}]+\xi_{it}$, notice that $\xi_{it}$ is independent of any information set at t-1. Thus we get the moment condition $E[\xi_{it}k_{it}]=0$, then we can use method of simulating moments to estimate $\beta_k$.
		\begin{itemize}
			\item The key assumption in first step is, current period investment $i_t$ can be represented by a function of $f(k_t,\omega_t)$. 
			If $f$ is invertible in $\omega_t$ (for example, $f$ being monotone in $\omega$), then we can write $\omega$ as a function of $(i_t, k_t)$.
		\end{itemize}

		\item LP is very similar to OP, just that use intermediate input $m_{it}$ instead of investment $i_{it}$ in proxy $\omega_{it}$. Because OP approach requires the policy function of $i_{it}$ be monotonicity in $\omega_{it}$, which is unsatisfied when $i_{it}=0$. But data shows that in many observations $i=0$. Using intermediate input can solve this.

		\item ACF criticizing is that $\beta_l$ cannot be identified in the first step. In LP we assume that $m_{it}=f_t(k_{it},\omega_{it})$. But we can reasonably argue by the same reason that $l_{it}=h_t(k_{it},\omega_{it})$. Then since $f(\cdot)$ is invertible, then we can write $l_t$ as some deterministic function of $k_{it}$ and $m_{it}$. This implies we cannot identify $\beta_l$ in the first step. The solution of ACF is to identify both $\beta_k$ and $\beta_l$ simultaneously at step 2, which is feasible since we now have two moment conditions.
	\end{itemize}
	\item \cite{Gandhi:2017un} Approach (GNR). GNR criticizes control function approach is nonparametrically not identified in the presence of flexible inputs. They raise a new approach using FOC conditions.
\end{itemize}

@@

\section{Demand Function Estimation} % (fold)
\label{sec:demand_function_estimation}

\noindent
\textbf{Reference:} \cite{shum:2016bk} CH 1 is very good for motivation and techniques.\\

\noindent
\textbf{Motivation for demand estimation}
\begin{itemize}
	\item Firstly, it is important per se, we want to understand consumer behaviour. And we want to \textit{predict the results of price change}, and \textit{introduction of new products}. 
	Such counter factual predictions can only be built upon a structural model.
	\item Secondly, estimation of demand function helps us better understand market structure. Markup itself is rarely observed (with some exceptions, like the electronic industry), but we can generally observe demand elasticity.
	Recall that $\frac{p-MC}{p}=1/\varepsilon$ (see \ref{sec:rey_and_stiglitz_1995_rand}). Estimation of $\varepsilon$ will help us know the markup of firm, thus infer market structure.
\end{itemize}

\noindent
\textbf{Challenges in demand function estimation:}
\begin{itemize}
	\item Too many parameters. Think of a market with 100 commodities and we want to estimate the cross elasticities. The number of parameters will be 10,000. Obviously it is impossible to have enough data to estimate so many parameters.
	\begin{itemize}
		\item Solved by nested logit model.
	\end{itemize}
	\item Unobserved quality. This will causes the endogeneity of price. And because the unobservable quality affects the selling in a highly nonlinear way, so IV is not very applicable in this case.
	\begin{itemize}
		\item Solved by BLP style estimation.
	\end{itemize}
\end{itemize}

\subsection{Brief Literature Review} % (fold)
\label{sub:brief_literature_review}

There are two branches of demand function estimation.
The early literature features differentiated goods (continuous choices). Classical examples include \cite{Hausman:1994km} introducing a nested approach to reduce the dimension of parameters.

Recent literature focus much more on discrete choice model. The seminal papers are \cite{Berry:1994jh} and \cite{berry.et.al.1995.emca}.
The address of these two papers is to overcome the \textbf{endogenous price problem due to unobserved quality}. 
Suppose we use a characteristic approach, where consumer utility and thus their purchase decision is decided by characteristics of products. 
Some of the characteristics are obervable to consumer (and firms) but not to econometricians, for example the advertisement. 
For higher unobserved quality, the equilibrium price will be higher, leading to a downward bias of price elasticity.

\cite{Berry:1994jh} comes with a method to overcome this endogeneity problem with only \textit{market level data}.
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\item The basic idea is a IV based two step estimation.
	\item First step: denote $\delta_j$ to be the `mean utility' for brand $j$. Notice this includes unobserved quality. Under some conditions, $\delta_j$ can be \textit{inversed} by market shares $(s_1,...,s_J)$, and thus we can get $\hat \delta_j$ by observed market shares. 
	\textcolor{blue}{This inversion step is the key for this paper, and many following papers treating endogenous quality problem.}
	\item Second step: By definition, $\delta_j=X_j\beta -\alpha p +\xi_j$. Thus we can get $\hat \xi_j$ if we get $\hat \delta_j$. Suppose $E[\xi Z]=0$, then we can use $Z$ as IV to estimate consistently.
\end{itemize}

\cite{berry.et.al.1995.emca} (BLP henceforce) is more comprehensive with the same idea. They introduce random-coefficients logit model, which allows each individual to have different taste coefficients. Thus we can't directly use the inverse technique. The way is to use a Simulation Method of Moments (inner loop and outer loop). First guees a $\delta$, match mkt share, then run a IV regression, then guess different $\delta$ and get an outer loop. They prove a contraction mapping.

\myline

\textbf{\bibentry{Quan_Williams:2017wp}}

This paper addresses the local heterogeneity of consumer demand,
and concludes that usual BLP method will overestimate the welfare increase of e-commerce because local stores have satisfied most local demands.\\

\noindent
\textbf{Challenges:}
\begin{itemize}
	\item Huge varieties of goods in fine-grid locations make scarce data in each category. Two possible solutions for this: 1) aggregating over locations; 2) just ignore the zero sales. 
	Aggregating is unsatisfactory since the heterogeneity of local preference is our study focus.
	Ignoring will cause selection bias and cause overestimation of local heterogeneity.
	\item Mean utility level cannot be recovered solely by observable variables.
	They raise specific Converging in Distribution theorem to tackle this.
\end{itemize}

% subsection brief_literature_review (end)

% section demand_function_estimation (end)

\section{Price Dispersion} % (fold)
\label{sec:price_dispersion}

\textbf{\bibentry{Baye:2013un}}

\begin{itemize}
	\item Price comparing sites becoming less popular,
	more consumers choose to direcly go to like Amazon and eBay.
	These websites also have `marketplace'.
	\item Many searching behaviour are not observed. Non-texture data (e.g. in the menu, directories).
	\item Search time across platforms can hardly be compared.
	Because maybe it's enough to search only once in Amazon, 
	but many times in eBay.
\end{itemize}

\myline

\noindent
\textbf{Random Ideas}
\begin{itemize}
	\item Collusion when there is consumer searching cost.
	Intuitively, collusion should be easier to sustein with 
	\textcolor{blue}{[no idea]}

	\item Awaya-Krishna (2016) 
\end{itemize}

% section price_dispersion (end)

\section{Multisided Platforms} % (fold)
\label{sec:multisided_platforms}

\textbf{\bibentry{Evans_Schmalensee:2012wp} }
\begin{itemize}
	\item Price structure matters. Reduce charge by one side and increase charge by another side will affect the transaction.
	\item Transaction cost is necessarily high for multisided platform.
	\item Two kind of externalities. Usage externality and membership externality.
	\item Pricing is compelicated. Per-transaction fee, or membership-fee. \textcolor{blue}{This looks similar to conventional IO model.}
	\begin{itemize}
		\item In per-transaction fee case. Price is directly proportional to the elasticity, while in conventional models price is inversely related to elasticity.
		\[\frac{p_1+p_2-c_1-c_2}{c_1+c_2}=\frac{1}{e_1+e_2}\]
		\[\frac{p_1}{e_1}=\frac{p_2}{e_2}\]
		Notice the second equation is unconventional.
		\item In membership-fee case.
		\item Both models can lead to a highly skewed price structure.
	\end{itemize}
	\item Competition Structure.
	\begin{itemize}
		\item Product differentiation
		\item Multi-home.
		\item Asymetric Competition. A n-sided platform may face competition from 1) one-sided firms; 2) a multisided platform competing in some but not all sides; 3) a multisided platform that has additional sides
	\end{itemize}
\end{itemize}

\myline

\textbf{Random Ideas}
\begin{itemize}
	\item Multisided platform as a commitment device changes the game structure. Like in the Truck-GasStation case raised in the book, the fleet-card company provides commitment power to the card companny, no renegotiation problem.
\end{itemize}

% section multisided_platforms (end)

\section{Erdem-Keane, 96 MktSci} % (fold)
\label{sec:erdem_keane_96_mktsci}

\textbf{\bibentry{erdem_kean:96_MngSci}}

\cite{erdem_kean:96_MngSci} provides an example on how to estimate demand when quality is uncertain and consumer learns by Bayesian rule.

\vspace{2mm}
\noindent
\textbf{Motivation:}
\begin{itemize}
	\item Avoide ad hoc assumptions on how consumers utilizing experience information
	\item Estimate structural models to do policy analysis
\end{itemize}

\noindent
\textbf{Features:}
\begin{itemize}
	\item Estimate Dynamic Programming.
	Consumers make decision based on their perceptions,
	but econometricians only observe the consumption. 
	So have to integrate over the distribution of perception errors $v_{ij}(t)$, which is is a Markov process.
	The integration part will be very complicated.
	\begin{itemize}
		\item Provides a way to estimate Dynamic Programming model with simulation. Also see \cite{keane_wolpin:94REStat}.
	\end{itemize}
	\item Experience Shocks.
	This indicates that even after purchasing once, 
	consumer is not certain about the quality of the good (or the preference of himself).
	This is mainly motivated by empirical fact: 
	consumption behavior generally do not converge.
\end{itemize}

\noindent
\textbf{Empirical Findings:}
\begin{itemize}
	\item Bayesian learning very well fit the date.

\end{itemize}

% section erdem_keane_96_mngsci (end)

\section{Gentzkov-Shapiro-Taddy, 17 WP} % (fold)
\label{sec:gentzkov_shapiro_taddy_17_wp}

\textbf{\bibentry{Gentzkow:2017hb}}

\begin{itemize}
	\item Methods for analyzing high-dimensional choices decisions
	\begin{itemize}
		\item also see \bibentry{Gentzkow_el.al:17WP}
	\end{itemize}
	\item Index for measuring polarization
\end{itemize}

This is a methodology paper introducing how to analyze high-dimensional choices decisions. They show that traditional logit model has severe finite sample bias.
They also raise a index for measuring polarization.

\textcolor{red}{[TO BE ADDED]}

% section gentzkov_shapiro_taddy_17_wp (end)

@@

\chapter{Game Theory} % (fold)
\label{cha:game_theory}

\section{Important Tools} % (fold)
\label{sec:important_tools}

\begin{thm}[Revelation Principle, Myerson, 1981]
Suppose that $\psi$ was a Bayes Nash equilibrium of the indirect mechanism $\Gamma$. 
Then there exists a direct mechanism that is payoff-equivalent and where truthful revelation is an equilibrium.
\end{thm}

\begin{myproof}
[to be added]
\end{myproof}

\begin{singlespacing}
\noindent
\textit{Comment:}
\end{singlespacing}
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\item Revelation Principle is defined over some specific solution concept. Here it is Bayes Nash Eqm.
	\item Revelation principle is not always satisfied. The stronger solution concept we use, the more likely it is not satisfied.
\end{itemize}

\subsection{Solution Concept} % (fold)
\label{sec:solution_concept}

There are many solution concepts:
\begin{itemize}
	\item Nash eqm
	\item Subgame Perfect eqm
	\item Perfect eqm
	\item $\varepsilon$-Perfect eqm
	\item Proper eqm
	\item Trembling-Hand eqm
	\item Bayesian Nash eqm
	\item (Weak) Perfect Bayesian eqm
	\item Sequential eqm
	\item Forward looking eqm
	\item Self-Confirming eqm

\end{itemize}

\begin{defn}[Self-confirming Equilibrium, \cite{Fudenberg_Levine:93EMCAa}]
Profile $\sigma$ is a \textit{self-confirming equilibrium} if for each player i, $s_i \in$ support($\sigma_i$) there exists belief $\mu_i$ such that:
\begin{enumerate}
	\item $s_i$ maximizes $u_i(\dot,\mu_i)$, and
	\item $\mu_i[\{\pi_{-i}|\pi_j(h_j)=
	\hat \pi_j(h_j|\sigma_j)\}]=1$, for all $j \neq i$ and $h_j \in \bar H(s_i,\sigma_-i)$, where $\bar H$ is the set of info sets that are reached with positive probability
\end{enumerate}
\end{defn}

\begin{singlespacing}
\noindent
\textit{Comment:}
\end{singlespacing}
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\item This definition mainly requires that the belief $\mu_i$ is consistent only at information sets that are reached with positive probability when player $i$ plays $s_i$.
	\item This is most obvious when contrast with Nash Eqm, which is almost the same as this definition,
	except for the consistency requirement is for all $h_j \in H_{-i}$. The consistency is required  for all information sets.
	\item Self-confirming is a weaker solution concept than Nash Equilibrium. 
	It uses the idea that players can only learn through what they observe.
	For those outcomes that they cannot observe,
	there is no particular reason for their beliefs to coincide.
	Players can never learn something they lack information on.
\end{itemize}

\begin{exmp}

\end{exmp}

% subsection solution_concept (end)

% section important_tools (end)

\section{Learning Theory} % (fold)
\label{sec:learning_theory}

\subsection{Important tools in learning} % (fold)
\label{sub:important_tools_in_learning}

\begin{defn}[Monotone Likelihood Ratio Property]
For all $l<S$,

\[\frac{p_{q,l}}{p_{q+1,l}} \geq \frac{p_{q,l+1}}{p_{q+1,l+1}} \ for \ all \ q<R\]
with strictly inequality for at least one q.

\end{defn}

This is first raised by \cite{Milgrom:1981dv}, which ensures that the conditional expectation of each individual increases in his signal realization.

\begin{defn}[Martingale]
A \textit{martingale} is a pair $(X_n,\F_N)$, where $\{\F_n\}$ is a filtration and $X_n$ an integrable (i.e. $E|X|<\infty$) stochastic process adapted to this filtration, such that 
\[E[X_{n+1}|\mathcal{F}_n]=X_n,\ a.s. \ \forall n\]
\end{defn}

\noindent
\textit{Comment:}
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\item Notice that Martingale process is much more restricted than Markov process, not only in the realization of expectation value. Markov process requires that 
	\[Pr(X_{t+1}\in A)|X_t=x_0,X_{t-1}=x_{t-1},...,X_{t-k}=x_{t-k}
	=Pr(X_{t+1}\in A)|X_t=x_0\]
	for all $A \in \mathcal{X}$, all $x_0,x_1,...,x_k \in \mathbb{X}$, and all $0\leq k\leq t$. 
	\begin{itemize}
		\item This actually restricts all stochastic properties, including expectations, variations and others.
		\item Also, Martingale process require conditional on $\F_t$, but Markov process only requires $x_t$.
	\end{itemize}
\end{itemize}

\begin{thm}[Martingale Convergence Theorem]

\end{thm}

% subsection important_tools_in_learning (end)

\subsection{Overview of literature} % (fold)
\label{sub:overview_of_literature}

% subsection overview_of_literature (end)

\textcolor{red}{The equilibrium concept used in literature is Bayesian Nash Eqm. Thus we put no restriction on off-eqm path beliefs. Nageeb said something about this, but I don't understand why this is important.}

\cite{Bikhchandani:1992fs} (BHW here after) is one of the original papers for learning in games. The main point is to explain the easily formulated but fragile information cascade when only actions are observed. The idea is, if only actions are observed, then after some threshold, private information will not affect action. And this private will NOT join the information pool, thus all following individual's private information will not contribute to the action. But since very little information is needed to form a cascade, this cascade can also be easily reversed when some shocks happen.

\cite{Smith:2000tz} is a generalization of BHW paper. The generalization lies in these aspects:
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\item Heterogeneity in quality of information (possibly unbounded private information)
	\item Heterogeneity of preference (noise by crazy types)
	\item Information cascade is NOT a generic feature; but 'herding' is.
	\item Necessary and sufficient condition for \textit{complete learning}.
\end{itemize}
This paper also provides a general approach on how to handle learning behaviour.
% section learning_theory (end)

\subsection{Bikhchandani-Hirshleifer-Welch, 92 JPE} % (fold)
\label{subsec:bikhchandani_hirshleifer_welch_92_jpe}

\textbf{\bibentry{Bikhchandani:1992fs}}

BHW is the seminal paper of social learning, which explains imitating in social phenomena without any ad hoc assumptions. By ad hoc assumptions, I means following:
\begin{itemize}
	\setlength{\itemsep}{0pt}
	\item sanctions on deviants
	\item positive payoff externalities
	\item conformity preference
\end{itemize}
This assumptions all have the unsatisfying property that puts the cart before the horse.

\textcolor{red}{TO BE ADDED}

% section bikhchandani_hirshleifer_welch_92_jpe (end)

\subsection{Kremer-Mansour-Perry, 14 JPE} % (fold)
\label{subsec:kremer_mansour_perry_14_jpe}

\textbf{\bibentry{KMP:2014jpe}}

Different from previous learning papers, KMP focuses on the optimal information disclosure of planner.
They find that it is not always optimal for planner to disclose full information, because it will discourage agents' incentive to explore and exploration has positive externalities.

Example: Online review website like TripAdvisor, Yelp; Google Map\\

\noindent
\textit{Illustrative example:}

Say $R_1$ is uniformly distributed in $[-1,5]$, and $R_2$ is uniformly distributed in $[-5,-5]$.
Then agent-1 for sure will choose $a_1$ since its ex-ante expeted payoff is higher.
Planner cannot force agent-1 to choose $a_2$ because of IC condition.

If realized $R_1$ is lower than 0, then for sure agent-2 will choose $a_2$.
But planner can do better by recommending agnet-2 to play $a_2$ whenever $R_1 \leq 1$.
Agent-2 will follow this suggestion because the $E[R_1]$ is 0 conditional on planner not disclosing.

If unfortunately the realized $R_1$ is higher than 1, then there is no way to make agent-2 to choose $a_2$,
but it is still possible to ask agent-3 to explore if $R_1$ is not too high.
Because when player-3 is recommended to play $a_2$, she cannot distinguish between:
1) planner knows both realization and $R_2>R_1$;
or 2) planner wants her to explore.
The second situation is in the same shoes as agent-2,
but because of the possibility of the first situation,
agent-3 will admit a higher upper threshold for exploring.\\
$\hfill\square$

\vspace{2mm}
\noindent
\textit{\textbf{Main Results:}}
(The proof of this paper is not difficult, and worth learning)
\begin{itemize}
	\item The optimal policy is threshold policy. For each individual, there is an interval of realization $r_1$ such that he is the first agent to explore.
	\item There is an upper bound of exploration time, which is independent of agents number $T$ and realization of $R_1,R_2$.
	This indicates result will converge to first best when $T$ is large enough.
\end{itemize}

\vspace{2mm}
\noindent
\textit{\textbf{Comments:}}
\begin{itemize}
	\item Generalize action to $n$ will not affect the structure of optimal policy. While continuum of action will ask for new setting. See referee report for more.

	\item We can also think the realization of $R_1$ and $R_2$ is \textbf{correlated}. 
	The result of this paper will not hold in this case.
	Think of the extreme case that correlation between $R_1$ and $R_2$ is $-1$.
	Then for any $R_1>0$, the planner will never explore $a_2$. For any $R_1<0$, the planner will recommend $a_2$ for all agents except for first one, and they will accept this recommendation.
	The correlation problem also exists when the relization of $R_i$ is not a value but a distribution, in the sense of correlation in mean value. In another direction, if the realization is positively correlated, then the exploration cost will be lower. And optimal policy should have lower upper threshold for each agent.
	\vspace{1mm}

	I think this extension important, because we have correlations in many real world applications.
	Take TripAdvisor as an example. If we already have reviews on one Marriott hotel in Paris, then it's not very useful to explore another Marriott at Toulouse! 
	Intuitively, planner should utilize such correlation, and put more weight on exploration of independent realizations.
	The optimal policy could be interesting.

	\item I also think of how this can be combined with optimal persuasion.
	If planner and agents have discrepancy in interest, 
	then persuasion is needed.
\end{itemize}

% section kremer_mansour_perry_14_jpe (end)

\section{Hard Information} % (fold)
\label{sec:hard_information}

\noindent
\textbf{Unraveling:}

\textit{Unraveling} is first discussed by \cite{Grossman:1981ih} and \cite{Milgrom:1981dv}. 
They show that if investor knows the type of firm's information, 
such information is perfectly verifiable at no cost, and the disclosure of such information is at no cost.
Then exist a sequential equilibrium, where the firm will disclose all information, good or bad.
The intuition is, since investors know the type (distribution) of information firm has, the nondisclosure indicates a worst information.
If the investor is so suspicious, firm will disclose those not so good information.

\cite{Dye:1985a} finds that such unraveling may not always happen.
There are many possible reasons, basically they are violations of above three assumptions.

\cite{Quigley:2017us} discusses unraveling in existence of outside information. They show that such information beyond control of insiders will \textit{reverse} unraveling result.
The highest quality insiders remain quiet, and only the mediocre insiders disclose information.
Notice that sending message is costly in this model.
The intuition for this result is,
when type is high enough,
outside information is enough to persuade the outsider.
My guess is,
this holds because the outsider decision is not fully divisible.

\myline
\noindent
\textbf{Mechanism Design with Hard Information:}

\cite{galzer_ruinstein:emca04} discusses the optimal decision rule when listener can check only one value.
\textcolor{blue}{[Not yet read]}

\cite{Green:1986gs} discusses the direct mechanism under partially verifiable information. 
They show that the \textit{Nested Range Condition} is necessary and sufficient for all socially-implementable mechanisms to be truthfully-implementable mechanisms.
The condition requires that if A can pretend to be B,
B can pretend to be C, then A can pretend to be C.
This condition is used in many other papers like \cite{Hart_et:17aer_evidence_games}, and monotonicity condition in \cite{Grossman:1981ih} is also included.
But notice that their paper does not consider a explicit checking process, so the result cannot apply to \cite{BenPorath:2014bc}, where a perfect but costly checking technique exists.

\subsection{Evidence Game} % (fold)
\label{sub:evidence_game}

\textcolor{blue}{[Below is based on the talk by Xiao]}
The paper by \cite{Hart_et:17aer_evidence_games} provides a general framework for evidence games. It shows that under conditions:
\begin{itemize}
	\item A1. $\theta \in m(\theta) \subseteq \Theta$.
	It basically restricts the message space to be the type space, and every can truthfully report his own type.
	\item A2. If $\theta' \in m(\theta'')$ and $\theta \in m(\theta')$, then $\theta \in m(\theta'')$. It means the masquerade is transitive, which is quite restrictive condition.
\end{itemize}
With above two assumptions, and \textit{truth-leaning} refinement of equilibriums, they show that giving receiver commitment power will make him no strict better off.

Many more basic models like \cite{Dye:1985a} and \cite{Milgrom:1981dv} can be encompassed by this framework. \textcolor{blue}{[Worth trying to put them in.]}

% subsection evidence_game (end)

\subsection{Beyer-Cohen-Lys-Walther, 10 JAcctE} % (fold)
\label{sub:beyer_cohen_lys_Walther_10_jaccte}

\textbf{\bibentry{Beyer:2010cj}}

This paper surveys literature of \textbf{voluntary information disclosure}, which is highly correlated with \textit{hard information} literature we discuss in reading group. I mainly read the section 3 (voluntary disclosure) of this paper.
